\vspace{-2cm}A generative model for urban firm networks

### 2020-09-01 main.tex
Update on Overleaf.

When considering optimal points with $\varepsilon_L < 5.0$, the adjusted parameters are: long range gravity interactions and socio-economic interactions given by $d_0 = 5205 \pm 1775$ and $c_0 = 109 \pm 29$ (the maximal $c_{ij}$ is 11.8); a stronger influence of destination than origin as $\gamma_O = 1.45 \pm 0.09$ and $\gamma_D = 2.0 \pm 0.06$; a comparable influence of sectors as $\gamma_S = 1.75 \pm 0.17$; a fine time granularity as $t_f = 4960 \pm 109$; and a very strong influence of previous links as $\gamma_W = 7.99 \pm 3.77$. This last point furthermore shows in particular a role of the path-dependency parameter, confirming the relevance of this complex generative model including path-dependency. The interaction of this process with others implies an inversion of the relative importance of origin and destination (on the contrary to statistical models). The fact that calibrated interaction distances are large is consistent with long range economic interactions within Europe. Besides these stylized facts, these calibration results altogether demonstrate the feasibility of model application to real data.

>>>>

When considering optimal points with $\varepsilon_L < 5.0$, the adjusted parameters are: long range gravity interactions and socio-economic interactions given by $d_0 = 5972 \pm 2148$ and $c_0 = 113 \pm 33$ (the maximal $c_{ij}$ is 11.8); a stronger influence of destination than origin as $\gamma_O = 1.46 \pm 0.10$ and $\gamma_D = 2.0 \pm 0.05$; a comparable influence of sectors as $\gamma_S = 1.76 \pm 0.21$; a fine time granularity as $t_f = 4951 \pm 124$; and a very strong influence of previous links as $\gamma_W = 6.43 \pm 4.11$. This last point furthermore shows in particular a role of the path-dependency parameter, confirming the relevance of this complex generative model including path-dependency. The interaction of this process with others implies an inversion of the relative importance of origin and destination (on the contrary to statistical models). The fact that calibrated interaction distances are large is consistent with long range economic interactions within Europe. Besides these stylized facts, these calibration results altogether demonstrate the feasibility of model application to real data.
